Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-17 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:17	14:06:04	(Mon17.Aug)
la2pdf commit - 2015:08:17	14:36:33	(Mon17.Aug)

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% GLOSSARY %
%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \makeglossaries
% \input{../../Library/glossary}

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \usepackage{yfonts}

% \graphicspath{submission/final/gfx/}

% 
% %%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% % MACROS %       
% %%%%%%%%%%                                      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% 
% \newcommand\Fig[1]{Fig.~\ref{#1}}
% 
% \newcommand\Grey[1]{{\color{Grey}#1}}
% \newcommand\Red[1]{{\color{Red}#1}}
% \newcommand\Blue[1]{{\color{Blue}#1}}
% \newcommand\DarkBlue[1]{{\color{DarkBlue}#1}}
% \newcommand\LightBlue[1]{{\color{LightBlue}#1}}
% \newcommand\Brown[1]{{\color{Brown}#1}}
% \newcommand\Green[1]{{\color{Green}#1}}
% \newcommand\SeaGreen[1]{{\color{SeaGreen}#1}}
% \newcommand\Yellow[1]{{\color{yellow}#1}}
% \newcommand\Orange[1]{{\color{orange}#1}}
% 
% \newcommand\nn{\nonumber\\}
% 
% \newcommand\nmat[1]{\begin{matrix}#1\end{matrix}}
% \newcommand\bmat[1]{\begin{bmatrix}#1\end{bmatrix}}
% \newcommand\case[1]{\begin{cases}#1\end{cases}}
% \newcommand\textbox[2]{\footnotesize\text{\parbox{#1}{\centering\emph{#2}}}}
% 
% \newcommand\rand{\text{rand}}
% \newcommand\randn{\text{randn}}
% \newcommand\rect{\text{rect}}
% \newcommand\sinc{\text{sinc}}
% \newcommand\tr{\text{tr}}
% \newcommand\adj{\text{adj}}
% 
% % \newcommand\max{\text{max}}
% \newcommand\argmin{\text{argmin}}
% 
% \newcommand\qqquad{\quad\qquad}
% \newcommand\qqqquad{\qquad\qquad}
% 
% \renewcommand\l[1]{\left#1}
% \renewcommand\r[1]{\right#1}
% 
% % {\text{\parbox{1.5cm}{\centering volume hyper- sphere}}}
% 
% %Keyword colouring:
% \newcommand\kw[1]{#1}
% \newcommand\parm[1]{#1}%\color{Black}#1\color{Black}}
% 
% \newcommand\of[1]{\scriptstyle(\parm{#1})\displaystyle}
% \newcommand\df[1]{\scriptstyle[\parm{#1}]\displaystyle}
% \newcommand\var[3]{#1_\text{#2}\of{#3}}
% 
% \newcommand\diag{\text{diag}}
% 
% % \raisebox{lift}[extend-above-baseline][extend-below-baseline]{text}
% \newcommand\mt[1]{\text{\emph{#1}}} %mt = mathtext
% \newcommand\mathnorm{\textstyle}
% \newcommand\mathbig[1]{\displaystyle#1\mathnorm}
% \newcommand\mathsmall[1]{\scriptstyle#1\mathnorm}
% \newcommand\mathtiny[1]{\scriptscriptstyle#1\mathnorm}
% \newcommand\sfrac[2]{\scriptstyle\raisebox{0.25pt}[0pt][0pt]{$\frac{#1}{#2}$}\mathnorm}
% \newcommand\nfrac[2]{\textstyle\frac{#1}{#2}\displaystyle}
% 
% \newcommand\sumu[1]{\sum\limits^{#1}\,}
% \newcommand\suml[1]{\sum\limits_{#1}\,}
% \newcommand\sumb[2]{\sum\limits_{#1}^{#2}\,}
% 
% \newcommand\produ[1]{\prod\limits^{#1}\,}
% \newcommand\prodl[1]{\prod\limits_{#1}\,}
% \newcommand\prodb[2]{\prod\limits_{#1}^{#2}\,}
% 
% %Math macros:
% \newcommand\diff[2]{\frac{\kw{d}\,\textstyle #1\scriptstyle}{\kw{d\parm{#2}}}\displaystyle}
% \newcommand\ddiff[2]{\frac{\kw{d^2}\,\displaystyle #1\scriptstyle}{\kw{d\parm{#2}}^2}\displaystyle}
% 
% \renewcommand\d[1]{\scriptstyle\kw{\,d\parm{#1}}\displaystyle}
% 
% % These commands are mutually exclusive. Remember to "renew" in v2.
% \newcommand\intb[4]{\int\limits_{#3}^{#4} #1 \d{#2}} % \int{exp}{var}{from}{to}
% \newcommand\intl[3]{\int\limits_{#3} #1 \d{#2}} % \int{exp}{var}{for all}
% \newcommand\intu[2]{\int #1 \d{#2}} % \int{exp}{var}{for all}
% 
% \newcommand\T{^{\scriptscriptstyle T}}
% \renewcommand\H{^{\scriptscriptstyle H}}
% 
% \renewcommand\vec[1]{\boldsymbol{#1}}
% \newcommand\mat[1]{\boldsymbol{#1}}
% 
% 
% \renewcommand*\a{\vec a}
% \renewcommand*\i{\vec i}
% \renewcommand*\k{\vec k}
% \newcommand*\n{\vec n}
% \newcommand*\p{\vec p}
% \newcommand*\s{\vec s}
% \newcommand*\w{\vec w}
% \newcommand*\x{\vec x}
% \newcommand*\y{\vec y}
% 
% \newcommand*\A{\mat A}
% \newcommand*\B{\mat B}
% \newcommand*\C{\mat C}
% \newcommand*\E{\mat E}
% % \renewcommand*\H{\mat H}
% \renewcommand*\P{\mat P}
% \newcommand*\eP{\mat{\hat P}}
% \newcommand*\R{\mat R}
% \newcommand*\Ri{\R^{-1}}
% \newcommand*\eR{\mat{\hat R}}
% \newcommand*\W{\mat W}
% \newcommand*\X{\mat X}
% \newcommand*\Xd{\X_{\!\Delta}}
% \newcommand*\Y{\mat Y}
% 
% \renewcommand*\L{\mat \Lambda}
% \newcommand*\U{\mat U}
% % \renewcommand*\t{\mathtiny{^T}}
% % \newcommand*\h{\mathtiny{^H}}
% \renewcommand*\t{^T}
% \newcommand*\h{^H}
% 
% \newcommand\D{\vec\nabla} %Del: Vector differential operator - nabla
% \newcommand\Dx{\vec\nabla\times}
% \newcommand\Dd{\vec\nabla\cdot}
% 
% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}
% \usepackage{amsmath,amssymb}
% 
% \newenvironment{outline}
% {\begin{itemize}}
% {\end{itemize}}

%    \definecolor{todobackground}{rgb}{0.95,0.95,0.95}
%    \setlength\marginparsep{3pt}
%    \setlength\marginparwidth{42pt}
%    \newlength\marginparwidthsmall
%    \setlength\marginparwidthsmall{\marginparwidth}
%    \addtolength\marginparwidthsmall{-7pt}
%    \newcommand\todo[1]{%
%       \addtocounter{todoidx}{1}%
%       {\color{Red}\fbox{\bf\thetodoidx{}}}%
%       \marginpar{%
%          {\vspace*{-10pt}\color{Red}\fbox{\bf\thetodoidx{}}}\\%
%          \fcolorbox{red}{todobackground}{\parbox{\marginparwidthsmall}{#1}}}}
%

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \RequirePackage[utf8]{inputenc}%              % Set input encoding (optionally latin1)
% \RequirePackage[T1]{fontenc}%                 % Set font encoding

@@

% Adaptive beamformers usually compute the window coefficients by estimating and inverting a spatial covariance matrix. There are two inherent problems to this procedure. First, for improved estimation accuracy the data is either averaged in space or time, and the significance of the covariance matrix can be reduced using a regularisation parameter~\cite{Carl Inge}. These are all attempts to constrain the beamformer to ensure the window coefficience are not over-adapted to the data. Second, inverting the covariance matrix has a computational complexity of O($M^3$)~\cite{Carl Inge}. For larger arrays the computational burden becomes significant, and the question arises whether this processing power can be better utilised.

@@

Let the receiver be an $M$ element uniform linear array. Call the the data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on.

By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. With static weights this would be referred to as the conventional delay-and-sum (DAS) beamformer. A large variety of weighting functions exists here for trading lateral resolution for improved noise suppression (contrast), but one always ends up with a compromise between the two~\cite{Harris1978}.

 coarse delay adjustment is usually achieved by applying delays to the sensor channels to negate the difference in travel time from the point of interest, and cause the  thereby aligning the phase of the signals coming from that source. Next a set of weights, or window, is applied to the sensors to Finally a set of weights  , which in effect achieve this by applying delays and weigths to the sensor channels to coherently combine signals from the direction of interest.

Let the array be an $M$ element uniform linear array,

@@

>>>>

@@

@@

Let the receiver be an $M$ element uniform linear array. Call the the data from the $m$th channel $x_m[\theta,n]$, where the azimuth angle $\theta$ and range sample $n$ is the focus point. To simplify notation, we make the dependence on $\theta$ implicit from now on. By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$.

With static weights this would be referred to as the conventional delay-and-sum (DAS) beamformer. A large variety of weighting functions exists here for trading lateral resolution for improved noise suppression (contrast), but one always ends up with a compromise between the two~\cite{Harris1978}.

@@

We limit our study to the use of variations of the parametric Kaiser-Harris window, since we observed neglible performance difference to using this function or any of the common trigonometric ones. The Kaiser windows are easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.
